---
title: "Multiple Lines of Evidence for the Effects and Sources of PAHs"
author: "Samantha Oliver"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

There are several techniques that can be used to identify the sources of contaminants in the 
environment. For polycyclic aromatic hydrocarbons (PAHs), there is no one perfect test, and many
methods have limitations. However, taken together, a multiple-lines-of-evidence approach can
give us more confidence in the sources of these contaminants in the environment. This package uses
common PAH input data (source profiles, sample profiles) and generates the analyses and figures 
of the multiple-lines-of-evidence approach used by Baldwin et al. 2017. 

## Package Overview

The package can produce the analyses and figures required for 7 of the 8 lines of evidence
used by Baldwin et al. (2017). The primary input into the package is either a set of USGS site IDs that can be used to call data from NWIS using `getPAH` which is a wrapper for functions in the package `dataRetrieval`, or a spreadsheet of PAH concentration data with corresponding site IDs. `processPAH` can take your PAH data and do common tasks, like deciding what to do with nondetects or values below detection limit, and modifying the dataframe from a wide to long format, and vice versa. 

## Step 1: Basic Visualizations of the Data

An important first step is to visualize the data to see the magnitude and ranges of PAH concentrations by different compounds and sites. This can be accomplished using the `PAHbysite` function. If your dataset includes a grouping ID (e.g., sites nested within watershets), you can order and label the data by groups.  

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
